\pkg{casebase}: An Alternative Framework For Survival Analysis and Comparison of Event Rates

### 2020-09-20 analysis/paper/paper.Rmd
updated abstract, CS3 figure legends

---
documentclass: jss
author:
  - name: Sahir Rai Bhatnagar*
    affiliation: McGill University
    address: >
      1020 Pine Avenue West
      Montreal, QC, Canada H3A 1A2
    email: \email{sahir.bhatnagar@mail.mcgill.ca}
    url: http://sahirbhatnagar.com/
  - name: Maxime Turgeon*
    affiliation: 'University of Manitoba \AND'
    address: >
      186 Dysart Road
      Winnipeg, MB, Canada R3T 2N2
    email: \email{max.turgeon@umanitoba.ca}
    url: https://maxturgeon.ca/
  - name: Jesse Islam 
    affiliation: McGill University
    address: >
      1020 Pine Avenue West
      Montreal, QC, Canada H3A 1A2
    email: \email{jesse.islam@mail.mcgill.ca}
  - name: James A. Hanley
    affiliation: McGill University
    address: >
      1020 Pine Avenue West
      Montreal, QC, Canada H3A 1A2
    email: \email{james.hanley@mcgill.ca}
    url: http://www.medicine.mcgill.ca/epidemiology/hanley/
  - name: Olli Saarela
    affiliation: University of Toronto
    address: >
      Dalla Lana School of Public Health, 
      155 College Street, 6th floor, 
      Toronto, Ontario 
      M5T 3M7, Canada
    email: \email{olli.saarela@utoronto.ca}
    url: http://individual.utoronto.ca/osaarela/
title:
  formatted: "\\pkg{casebase}: An Alternative Framework For Survival Analysis and Comparison of Event Rates"
  # If you use tex in the formatted title, also supply version without
  plain:     "casebase: An Alternative Framework For Survival Analysis and Comparison of Event Rates"
  # For running headers, if needed
  short:     "\\pkg{casebase}: An Alternative Framework For Survival Analysis"
abstract: |
  | In epidemiological studies of time-to-event data, a quantity of interest to the clinician and the patient is the risk of an event given a covariate profile. However, methods relying on time matching or risk-set sampling (including Cox regression) eliminate the baseline hazard from the likelihood expression or the estimating function. But to estimate risks, the baseline hazard needs to be estimated separately using a non-parametric method. This apparoch leads to step-wise estimates of the cumulative incidence that are difficult to interpret. Using case-base sampling, Hanley & Miettinen explained how the parametric hazard functions can be estimated using logistic regression. Their approach naturally leads to estimates of the cumulative incidence that are smooth-in-time.
  | In this paper, we present the casebase R package, which implements the ideas of Hanley & Miettinen through a simple and flexible interface. We describe how the case-base framework can also be used in more complex settings: competing risks, time-varying exposure, and variable selection. Our package also includes an extensive array of visualization tools to complement the analysis of time-to-event data. We illustrate all these features through four different case studies.
  | *SRB and MT contributed equally to this work.
keywords:
  # at least one keyword must be supplied
  formatted: [survival analysis, absolute risk, "\\proglang{R}", data visualization]
  plain:     [survival analysis, absolute risk, R, data visualization]
preamble: >
  \usepackage{amsmath}
  \usepackage{amssymb}
  \usepackage{longtable}
  \usepackage{graphicx}
  \usepackage{tabularx}
  \usepackage{float}
  \usepackage{booktabs}
  \usepackage{makecell}
  \usepackage{tabu}
  \DeclareUnicodeCharacter{2500}{-}

@@

```{r coefplots, echo=FALSE, eval=eval_cs3, fig.cap="\\label{fig:cs3lolliPlot} Lollipop plot showing the coefficient estimates between three models. Only covariates common among all three models were retained. Shrinkage occurs due to penalization."}
library(dotwhisker)
library(broom)
library(dplyr)

@@

```{r riskregressionBrier, echo = FALSE, eval = eval_cs3, fig.cap="\\label{fig:cs3FinalBrier} Comparison of Cox regression, penalized Cox regression, penalized case-base estimation, and Kaplan-Meier. (A)  Probabilities of death as it changes over follow-up time. (B) Brier scores as they change over time, where a lower score corresponds to better performace.", warning = FALSE}
# Combine scores
data_brier <- bind_rows(
  brierCoxKM$Brier$score %>% 
    mutate(model = as.character(model)) %>% 
    filter(model != "Null model"),
  brierPenalized$Brier$score %>% 
    mutate(model = as.character(model)) %>% 
    filter(model != "Null model")
  ) %>% 
  mutate(model = factor(model, levels = c("Cox", "Pen. Cox", "Pen. CB", "K-M")))

>>>>

---
documentclass: jss
author:
  - name: Sahir Rai Bhatnagar*
    affiliation: McGill University
    address: >
      1020 Pine Avenue West
      Montreal, QC, Canada H3A 1A2
    email: \email{sahir.bhatnagar@mail.mcgill.ca}
    url: http://sahirbhatnagar.com/
  - name: Maxime Turgeon*
    affiliation: 'University of Manitoba \AND'
    address: >
      186 Dysart Road
      Winnipeg, MB, Canada R3T 2N2
    email: \email{max.turgeon@umanitoba.ca}
    url: https://maxturgeon.ca/
  - name: Jesse Islam 
    affiliation: McGill University
    address: >
      1020 Pine Avenue West
      Montreal, QC, Canada H3A 1A2
    email: \email{jesse.islam@mail.mcgill.ca}
  - name: James A. Hanley
    affiliation: McGill University
    address: >
      1020 Pine Avenue West
      Montreal, QC, Canada H3A 1A2
    email: \email{james.hanley@mcgill.ca}
    url: http://www.medicine.mcgill.ca/epidemiology/hanley/
  - name: Olli Saarela
    affiliation: University of Toronto
    address: >
      Dalla Lana School of Public Health, 
      155 College Street, 6th floor, 
      Toronto, Ontario 
      M5T 3M7, Canada
    email: \email{olli.saarela@utoronto.ca}
    url: http://individual.utoronto.ca/osaarela/
title:
  formatted: "\\pkg{casebase}: An Alternative Framework For Survival Analysis and Comparison of Event Rates"
  # If you use tex in the formatted title, also supply version without
  plain:     "casebase: An Alternative Framework For Survival Analysis and Comparison of Event Rates"
  # For running headers, if needed
  short:     "\\pkg{casebase}: An Alternative Framework For Survival Analysis"
abstract: |
  | In epidemiological studies of time-to-event data, a quantity of interest to the clinician and the patient is the risk of an event given a covariate profile. However, methods relying on time matching or risk-set sampling (including Cox regression) eliminate the baseline hazard from the likelihood expression or the estimating function and therefore needs to be estimated separately using a non-parametric approach. This leads to step-wise estimates of the cumulative incidence that are difficult to interpret. Using case-base sampling, Hanley & Miettinen (2009) explained how the parametric hazard functions can be estimated using logistic regression. Their approach naturally leads to estimates of the cumulative incidence that are smooth-in-time.
  | In this paper, we present the **casebase** R package, a comprehensive and flexible toolkit for parametric survival analysis. We describe how the case-base framework can also be used in more complex settings: competing risks, time-varying exposure, and variable selection. Our package also includes an extensive array of visualization tools to complement the analysis of time-to-event data. We illustrate all these features through four different case studies.
  | *SRB and MT contributed equally to this work.
keywords:
  # at least one keyword must be supplied
  formatted: [survival analysis, absolute risk, "\\proglang{R}", data visualization]
  plain:     [survival analysis, absolute risk, R, data visualization]
preamble: >
  \usepackage{amsmath}
  \usepackage{amssymb}
  \usepackage{longtable}
  \usepackage{graphicx}
  \usepackage{tabularx}
  \usepackage{float}
  \usepackage{booktabs}
  \usepackage{makecell}
  \usepackage{tabu}
  \DeclareUnicodeCharacter{2500}{-}

@@

```{r coefplots, echo=FALSE, eval=eval_cs3, fig.cap="\\label{fig:cs3lolliPlot} Coefficient estimates from the Cox model (Cox), penalized Cox model using the \\pkg{glmnet} package (Pen. Cox), and our approach using penalized case-base sampling (Pen. CB). Only the covariates that were selected by both penalized approaches are shown. The shrinkage of the coefficient estimates for Pen. Cox and Pen. CB occurs due to the $\\ell_1$ penalty."}
library(dotwhisker)
library(broom)
library(dplyr)

@@

```{r riskregressionBrier, echo = FALSE, eval = eval_cs3, fig.cap="\\label{fig:cs3FinalBrier} Comparison of Cox regression (Cox), penalized Cox regression (Pen. Cox), penalized case-base sampling estimation (Pen. CB), and Kaplan-Meier (K-M). (A)  Probability of death as a function of follow-up time. (B) Brier score as a function of follow-up time, where a lower score corresponds to better performace.", warning = FALSE}
# Combine scores
data_brier <- bind_rows(
  brierCoxKM$Brier$score %>% 
    mutate(model = as.character(model)) %>% 
    filter(model != "Null model"),
  brierPenalized$Brier$score %>% 
    mutate(model = as.character(model)) %>% 
    filter(model != "Null model")
  ) %>% 
  mutate(model = factor(model, levels = c("Cox", "Pen. Cox", "Pen. CB", "K-M")))

### 2020-09-20 analysis/paper/paper.tex
updated abstract, CS3 figure legends

\Abstract{
In epidemiological studies of time-to-event data, a quantity of interest
to the clinician and the patient is the risk of an event given a
covariate profile. However, methods relying on time matching or risk-set
sampling (including Cox regression) eliminate the baseline hazard from
the likelihood expression or the estimating function. But to estimate
risks, the baseline hazard needs to be estimated separately using a
non-parametric method. This apparoch leads to step-wise estimates of the
cumulative incidence that are difficult to interpret. Using case-base
sampling, Hanley \& Miettinen explained how the parametric hazard
functions can be estimated using logistic regression. Their approach
naturally leads to estimates of the cumulative incidence that are
smooth-in-time.\\
In this paper, we present the casebase R package, which implements the
ideas of Hanley \& Miettinen through a simple and flexible interface. We
describe how the case-base framework can also be used in more complex
settings: competing risks, time-varying exposure, and variable
selection. Our package also includes an extensive array of visualization
tools to complement the analysis of time-to-event data. We illustrate
all these features through four different case studies.\\
*SRB and MT contributed equally to this work.
}

@@

\begin{CodeInput}
R> pt_object <- casebase::popTime(ERSPC, time = "Follow.Up.Time",
+                                event = "DeadOfPrCa", exposure = "ScrArm")
R> inherits(pt_object, "popTime")
\end{CodeInput}

@@

\begin{CodeInput}
R> fmla <- list(exponential = as.formula(DeadOfPrCa ~ ScrArm),
+              gompertz = as.formula(DeadOfPrCa ~ Follow.Up.Time + ScrArm),
+              weibull = as.formula(DeadOfPrCa ~ log(Follow.Up.Time) + ScrArm),
+              splines = as.formula(DeadOfPrCa ~ bs(Follow.Up.Time) + ScrArm))
R> 
R> fits <- lapply(fmla, function(i) {
+   fitSmoothHazard(i, data = ERSPC, ratio = 100)
+ })
\end{CodeInput}
\end{CodeChunk}

@@

\begin{CodeInput}
R> new_data <- data.frame(ScrArm = c("Control group", "Screening group"))
R> new_time <- seq(0,14,0.1)
R> 
R> risks <- lapply(fits, function(i) {
+   absoluteRisk(object = i, time = new_time, newdata = new_data, method = "mont")
+ })
\end{CodeInput}
\end{CodeChunk}

@@

\caption{\label{tab:print-erspc-estimates}Comparison of estimated hazard ratios and 95\% confidence intervals for ERSPC data.}
\centering
\begin{tabular}[t]{>{}lcc}
\toprule
Model & casebase::fitSmoothHazard & survival::survreg\\
\midrule
\textbf{Exponential} & 0.79 (0.67, 0.94) & 0.81 (0.68, 0.96)\\
\cmidrule{1-3}
\textbf{Gompertz} & 0.80 (0.67, 0.95) & 0.80 (0.67, 0.95)\\
\cmidrule{1-3}
\textbf{Weibull} & 0.81 (0.68, 0.96) & 0.80 (0.65, 0.96)\\
\cmidrule{1-3}
\textbf{Splines} & 0.79 (0.66, 0.94) & --\\
\bottomrule
\multicolumn{3}{l}{\rule{0pt}{1em}Cox model estimate: HR (95\% CI) = 0.80 (0.67, 0.95)}\\
\end{tabular}
\end{table}

@@

\begin{CodeInput}
R> plot(fit_inter, type = "hr", newdata = new_data,
+      var = "ScrArm", xvar = "Follow.Up.Time", ci = TRUE)
\end{CodeInput}
\end{CodeChunk}

@@

\begin{CodeInput}
R> library(survival)
R> # Treat competing event as censoring
R> model_cox <- coxph(Surv(ftime, Status == 1) ~ Sex + D + Phase + Source + Age,
+   data = bmtcrr
+ )
\end{CodeInput}
\end{CodeChunk}

@@

\begin{CodeInput}
R> library(timereg)
R> model_fg <- comp.risk(Event(ftime, Status) ~ const(Sex) + const(D) +
+                         const(Phase) + const(Source) + const(Age),
+                       data = bmtcrr, cause = 1, model = "fg")
R> 
R> # Estimate absolute risk curve
R> risk_fg <- predict(model_fg, newdata, times = time_points)
\end{CodeInput}
\end{CodeChunk}

@@

\caption{\label{fig:cs3lolliPlot} Lollipop plot showing the coefficient estimates between three models. Only covariates common among all three models were retained. Shrinkage occurs due to penalization.}\label{fig:coefplots}
\end{figure}
\end{CodeChunk}

@@

This report was generated on 2020-09-16 10:30:17 using the following
computational environment and dependencies:

@@

\begin{CodeOutput}
#> R version 4.0.2 (2020-06-22)
#> Platform: x86_64-apple-darwin17.0 (64-bit)
#> Running under: macOS Catalina 10.15.6
#> 
#> Matrix products: default
#> BLAS:   /Library/Frameworks/R.framework/Versions/4.0/Resources/lib/libRblas.dylib
#> LAPACK: /Library/Frameworks/R.framework/Versions/4.0/Resources/lib/libRlapack.dylib
#> 
#> locale:
#> [1] en_CA.UTF-8/en_CA.UTF-8/en_CA.UTF-8/C/en_CA.UTF-8/en_CA.UTF-8
#> 
#> attached base packages:
#> [1] splines   stats     graphics  grDevices utils     datasets  methods  
#> [8] base     
#> 
#> other attached packages:
#>  [1] broom_0.7.0               dotwhisker_0.5.0         
#>  [3] timereg_1.9.7             glue_1.4.2               
#>  [5] scales_1.1.1              forcats_0.5.0            
#>  [7] stringr_1.4.0             dplyr_1.0.2              
#>  [9] purrr_0.3.4               readr_1.3.1              
#> [11] tidyr_1.1.2               ggplot2_3.3.2            
#> [13] tidyverse_1.3.0           lubridate_1.7.9          
#> [15] visreg_2.7.0              tibble_3.0.3             
#> [17] riskRegression_2020.02.05 prodlim_2019.11.13       
#> [19] flexsurv_1.1.1            survival_3.2-3           
#> [21] pracma_2.2.9              magrittr_1.5             
#> [23] kableExtra_1.2.1          glmnet_4.0-2             
#> [25] Matrix_1.2-18             data.table_1.13.0        
#> [27] cowplot_1.1.0             colorspace_1.4-1         
#> [29] casebase_0.9.0.9000      
#> 
#> loaded via a namespace (and not attached):
#>  [1] TH.data_1.0-10      VGAM_1.1-3          ellipsis_0.3.1     
#>  [4] ggstance_0.3.4      htmlTable_2.0.1     base64enc_0.1-3    
#>  [7] fs_1.5.0            rstudioapi_0.11     farver_2.0.3       
#> [10] MatrixModels_0.4-1  fansi_0.4.1         mvtnorm_1.1-1      
#> [13] xml2_1.3.2          codetools_0.2-16    knitr_1.29         
#> [16] Formula_1.2-3       jsonlite_1.7.1      cluster_2.1.0      
#> [19] dbplyr_1.4.4        png_0.1-7           compiler_4.0.2     
#> [22] httr_1.4.2          backports_1.1.9     assertthat_0.2.1   
#> [25] cli_2.0.2           htmltools_0.5.0     quantreg_5.67      
#> [28] tools_4.0.2         gtable_0.3.0        Rcpp_1.0.5         
#> [31] cellranger_1.1.0    vctrs_0.3.4         nlme_3.1-149       
#> [34] conquer_1.0.2       iterators_1.0.12    xfun_0.17          
#> [37] rvest_0.3.6         lifecycle_0.2.0     polspline_1.1.19   
#> [40] muhaz_1.2.6.1       MASS_7.3-53         zoo_1.8-8          
#> [43] hms_0.5.3           sandwich_2.5-1      SparseM_1.78       
#> [46] RColorBrewer_1.1-2  rticles_0.15        yaml_2.2.1         
#> [49] gridExtra_2.3       rms_6.0-1           rpart_4.1-15       
#> [52] latticeExtra_0.6-29 stringi_1.4.6       foreach_1.5.0      
#> [55] checkmate_2.0.0     lava_1.6.7          shape_1.4.4        
#> [58] rlang_0.4.7         pkgconfig_2.0.3     matrixStats_0.56.0 
#> [61] evaluate_0.14       lattice_0.20-41     labeling_0.3       
#> [64] htmlwidgets_1.5.1   cmprsk_2.2-10       tidyselect_1.1.0   
#> [67] deSolve_1.28        plyr_1.8.6          R6_2.4.1           
#> [70] generics_0.0.2      Hmisc_4.4-1         multcomp_1.4-13    
#> [73] DBI_1.1.0           withr_2.2.0         pillar_1.4.6       
#> [76] haven_2.3.1         foreign_0.8-80      mgcv_1.8-33        
#> [79] nnet_7.3-14         mstate_0.2.12       modelr_0.1.8       
#> [82] crayon_1.3.4        rmarkdown_2.3       jpeg_0.1-8.1       
#> [85] grid_4.0.2          readxl_1.3.1        blob_1.2.1         
#> [88] reprex_0.3.0        digest_0.6.25       webshot_0.5.2      
#> [91] numDeriv_2016.8-1.1 stats4_4.0.2        munsell_0.5.0      
#> [94] viridisLite_0.3.0   quadprog_1.5-8
\end{CodeOutput}
\end{CodeChunk}

@@

\begin{CodeOutput}
#> Local:    master /Users/maxturgeon/Documents/git_repos/cbpaper
#> Remote:   master @ origin (git@github.com:sahirbhatnagar/cbpaper.git)
#> Head:     [73c0393] 2020-09-15: update CS3
\end{CodeOutput}
\end{CodeChunk}

>>>>

\Abstract{
In epidemiological studies of time-to-event data, a quantity of interest
to the clinician and the patient is the risk of an event given a
covariate profile. However, methods relying on time matching or risk-set
sampling (including Cox regression) eliminate the baseline hazard from
the likelihood expression or the estimating function and therefore needs
to be estimated separately using a non-parametric approach. This leads
to step-wise estimates of the cumulative incidence that are difficult to
interpret. Using case-base sampling, Hanley \& Miettinen (2009)
explained how the parametric hazard functions can be estimated using
logistic regression. Their approach naturally leads to estimates of the
cumulative incidence that are smooth-in-time.\\
In this paper, we present the \textbf{casebase} R package, a
comprehensive and flexible toolkit for parametric survival analysis. We
describe how the case-base framework can also be used in more complex
settings: competing risks, time-varying exposure, and variable
selection. Our package also includes an extensive array of visualization
tools to complement the analysis of time-to-event data. We illustrate
all these features through four different case studies.\\
*SRB and MT contributed equally to this work.
}

@@

\begin{CodeInput}
R> pt_object <- casebase::popTime(ERSPC, time = "Follow.Up.Time",
R+                                event = "DeadOfPrCa", exposure = "ScrArm")
R> inherits(pt_object, "popTime")
\end{CodeInput}

@@

\begin{CodeInput}
R> fmla <- list(exponential = as.formula(DeadOfPrCa ~ ScrArm),
R+              gompertz = as.formula(DeadOfPrCa ~ Follow.Up.Time + ScrArm),
R+              weibull = as.formula(DeadOfPrCa ~ log(Follow.Up.Time) + ScrArm),
R+              splines = as.formula(DeadOfPrCa ~ bs(Follow.Up.Time) + ScrArm))
R> 
R> fits <- lapply(fmla, function(i) {
R+   fitSmoothHazard(i, data = ERSPC, ratio = 100)
R+ })
\end{CodeInput}
\end{CodeChunk}

@@

\begin{CodeInput}
R> new_data <- data.frame(ScrArm = c("Control group", "Screening group"))
R> new_time <- seq(0,14,0.1)
R> 
R> risks <- lapply(fits, function(i) {
R>   absoluteRisk(object = i, time = new_time, newdata = new_data, method = "mont")
R> })
\end{CodeInput}
\end{CodeChunk}

@@

\caption{\label{tab:print-erspc-estimates}Comparison of estimated hazard ratios and 95\% confidence intervals for ERSPC data.}
\centering
\begin{tabular}[t]{>{\bfseries}lcc}
\toprule
Model & casebase::fitSmoothHazard & survival::survreg\\
\midrule
Exponential & 0.79 (0.67, 0.94) & 0.81 (0.68, 0.96)\\
\cmidrule{1-3}
Gompertz & 0.80 (0.67, 0.95) & 0.80 (0.67, 0.95)\\
\cmidrule{1-3}
Weibull & 0.81 (0.68, 0.96) & 0.80 (0.65, 0.96)\\
\cmidrule{1-3}
Splines & 0.79 (0.66, 0.94) & --\\
\bottomrule
\multicolumn{3}{l}{Cox model estimate: HR (95\% CI) = 0.80 (0.67, 0.95)}\\
\end{tabular}
\end{table}

@@

\begin{CodeInput}
R> plot(fit_inter, type = "hr", newdata = new_data,
R>      var = "ScrArm", xvar = "Follow.Up.Time", ci = TRUE)
\end{CodeInput}
\end{CodeChunk}

@@

\begin{CodeInput}
R> library(survival)
R> # Treat competing event as censoring
R> model_cox <- coxph(Surv(ftime, Status == 1) ~ Sex + D + Phase + Source + Age,
R+   data = bmtcrr
R+ )
\end{CodeInput}
\end{CodeChunk}

@@

\begin{CodeInput}
R> library(timereg)
R> model_fg <- comp.risk(Event(ftime, Status) ~ const(Sex) + const(D) +
R+                         const(Phase) + const(Source) + const(Age),
R+                       data = bmtcrr, cause = 1, model = "fg")
R> 
R> # Estimate absolute risk curve
R> risk_fg <- predict(model_fg, newdata, times = time_points)
\end{CodeInput}
\end{CodeChunk}

@@

\caption{\label{fig:cs3lolliPlot} Coefficient estimates from the Cox model (Cox), penalized Cox model using the \pkg{glmnet} package (Pen. Cox), and our approach using penalized case-base sampling (Pen. CB). Only the covariates that were selected by both penalized approaches are shown. The shrinkage of the coefficient estimates for Pen. Cox and Pen. CB occurs due to the $\ell_1$ penalty.}\label{fig:coefplots}
\end{figure}
\end{CodeChunk}

@@

This report was generated on 2020-09-19 21:55:49 using the following
computational environment and dependencies:

@@

\begin{CodeOutput}
#> R version 4.0.2 (2020-06-22)
#> Platform: x86_64-pc-linux-gnu (64-bit)
#> Running under: Pop!_OS 20.04 LTS
#> 
#> Matrix products: default
#> BLAS:   /usr/lib/x86_64-linux-gnu/openblas-pthread/libblas.so.3
#> LAPACK: /usr/lib/x86_64-linux-gnu/openblas-pthread/liblapack.so.3
#> 
#> locale:
#>  [1] LC_CTYPE=en_US.UTF-8       LC_NUMERIC=C              
#>  [3] LC_TIME=en_US.UTF-8        LC_COLLATE=en_US.UTF-8    
#>  [5] LC_MONETARY=en_US.UTF-8    LC_MESSAGES=en_US.UTF-8   
#>  [7] LC_PAPER=en_US.UTF-8       LC_NAME=C                 
#>  [9] LC_ADDRESS=C               LC_TELEPHONE=C            
#> [11] LC_MEASUREMENT=en_US.UTF-8 LC_IDENTIFICATION=C       
#> 
#> attached base packages:
#> [1] splines   stats     graphics  grDevices utils     datasets  methods  
#> [8] base     
#> 
#> other attached packages:
#>  [1] broom_0.7.0               dotwhisker_0.5.0         
#>  [3] timereg_1.9.7             glue_1.4.2               
#>  [5] scales_1.1.1              forcats_0.5.0            
#>  [7] stringr_1.4.0             dplyr_1.0.2              
#>  [9] purrr_0.3.4               readr_1.3.1              
#> [11] tidyr_1.1.2               ggplot2_3.3.2            
#> [13] tidyverse_1.3.0           lubridate_1.7.9          
#> [15] visreg_2.7.0              tibble_3.0.3             
#> [17] riskRegression_2020.02.05 prodlim_2019.11.13       
#> [19] flexsurv_1.1.1            survival_3.2-3           
#> [21] pracma_2.2.9              magrittr_1.5             
#> [23] kableExtra_1.2.1          glmnet_4.0-2             
#> [25] Matrix_1.2-18             data.table_1.13.0        
#> [27] cowplot_1.1.0             colorspace_1.4-1         
#> [29] casebase_0.9.0           
#> 
#> loaded via a namespace (and not attached):
#>  [1] TH.data_1.0-10      VGAM_1.1-3          ellipsis_0.3.1     
#>  [4] ggstance_0.3.4      htmlTable_2.1.0     base64enc_0.1-3    
#>  [7] fs_1.5.0            rstudioapi_0.11     farver_2.0.3       
#> [10] MatrixModels_0.4-1  fansi_0.4.1         mvtnorm_1.1-1      
#> [13] xml2_1.3.2          codetools_0.2-16    knitr_1.29         
#> [16] Formula_1.2-3       jsonlite_1.7.1      cluster_2.1.0      
#> [19] dbplyr_1.4.4        png_0.1-7           compiler_4.0.2     
#> [22] httr_1.4.2          backports_1.1.9     assertthat_0.2.1   
#> [25] cli_2.0.2           htmltools_0.5.0     quantreg_5.67      
#> [28] tools_4.0.2         gtable_0.3.0        Rcpp_1.0.5         
#> [31] cellranger_1.1.0    vctrs_0.3.4         nlme_3.1-149       
#> [34] conquer_1.0.2       iterators_1.0.12    xfun_0.17          
#> [37] rvest_0.3.6         lifecycle_0.2.0     polspline_1.1.19   
#> [40] muhaz_1.2.6.1       MASS_7.3-53         zoo_1.8-8          
#> [43] hms_0.5.3           sandwich_2.5-1      SparseM_1.78       
#> [46] RColorBrewer_1.1-2  rticles_0.15        yaml_2.2.1         
#> [49] gridExtra_2.3       rms_6.0-1           rpart_4.1-15       
#> [52] latticeExtra_0.6-29 stringi_1.5.3       foreach_1.5.0      
#> [55] checkmate_2.0.0     lava_1.6.7          shape_1.4.5        
#> [58] rlang_0.4.7         pkgconfig_2.0.3     matrixStats_0.56.0 
#> [61] evaluate_0.14       lattice_0.20-41     labeling_0.3       
#> [64] htmlwidgets_1.5.1   cmprsk_2.2-10       tidyselect_1.1.0   
#> [67] deSolve_1.28        plyr_1.8.6          R6_2.4.1           
#> [70] generics_0.0.2      Hmisc_4.4-1         multcomp_1.4-13    
#> [73] DBI_1.1.0           withr_2.2.0         pillar_1.4.6       
#> [76] haven_2.3.1         foreign_0.8-79      mgcv_1.8-33        
#> [79] nnet_7.3-14         mstate_0.2.12       modelr_0.1.8       
#> [82] crayon_1.3.4        rmarkdown_2.3       jpeg_0.1-8.1       
#> [85] grid_4.0.2          readxl_1.3.1        blob_1.2.1         
#> [88] reprex_0.3.0        digest_0.6.25       webshot_0.5.2      
#> [91] numDeriv_2016.8-1.1 stats4_4.0.2        munsell_0.5.0      
#> [94] viridisLite_0.3.0   quadprog_1.5-8
\end{CodeOutput}
\end{CodeChunk}

@@

\begin{CodeOutput}
#> Local:    editSahir /home/sahir/git_repositories/cbpaper
#> Remote:   editSahir @ origin (https://github.com/sahirbhatnagar/cbpaper.git)
#> Head:     [d691836] 2020-09-19: Merge remote-tracking branch 'origin/master' into editSahir
\end{CodeOutput}
\end{CodeChunk}
